%----------------------------------------------------------------------------------------
%	TEACHING ASSISTANCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching Assistantship}

    \begin{rSubsection}{First Degree Teaching Assistant, Department of CSIS}{Aug 2023 --- Dec 2023}{BITS Pilani}{Goa, India}
    \item \textbf{CS F372 --- Operating Systems:} Assisted \textit{Prof.\ Biju K.R.} in conducting labs and tutorial classes in basic conceptsof C programming and Linux system calls. Prepared reading materials for labs and conducted doubt solving sessions.
    \item \textbf{CS F342 --- Computer Architecture:} Assisted \textit{Prof.\ Kanchan Manna} in conducting and evaluating weekly labs in HLD design labs in Verilog.
    \end{rSubsection}

    \begin{rSubsection}{First Degree Teaching Assistant, Department of CSIS}{Jan 2023 --- May 2023}{BITS Pilani}{Goa, India}
    \item \textbf{CS F211 --- Data Structures and Algorithms:} Assisted \textit{Prof.\ Sujith Thomas} in setting, testing and hosting weekly labs and evaluations for the course; conducted tutorial/problem solving sessions for students.
    \item \textbf{CS F342 --- Computer Architecture:} Assisted \textit{Prof.\ Amalin A.\ Prince} in conducting and evaluating weekly labs in Verilog based on MIPS and other architectures.
    \item \textbf{CS F424 --- Software for Embedded Systems:} Assisted \textit{Prof.\ Neena Goveas} in taking tutorials on Python and Android development.
    \end{rSubsection}

    \begin{rSubsection}{First Degree Teaching Assistant, Department of CSIS}{August 2022 --- Dec 2022}{BITS Pilani}{Goa, India}
    \item \textbf{CS F213 --- Object Oriented Programming:} Assisted \textit{Prof.\ Neena Goveas} in conducting and evaluating weekly labs based on Object Oriented concepts in Java; evaluated group projects and guided student teams toward implementing effective OOP principles.
    \item \textbf{CS F214 --- Logic in Computer Science:} Assisted \textit{Prof.\ A. Baskar} in conducting doubt solving sessions and guided students in weekly problem sheet solving.
    \end{rSubsection}

\end{rSection}